### 2019-12-19 ic-journal/coarsest.tex
Fixed a buggy sentence in Section 4.9, related to Klop processes

For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
defined on the natural numbers, we obtain a countable set of processes
with all Klop processes built from the same label.
Since the number of all Klop processes in this set is (countably) infinite, and
since they are all pairwise non-bisimiar,
we can always
choose a number that is mapped to a Klop process
that is non-bisimilar with any derivative of two given 
 (finite-state) processes $p$ and $q$,
even when $a$ is the only element of type $\beta$, i.e. the only label name
in $\mathscr{L}$.
This property is captured by appealing to the following set-theoreric
lamma (see~\cite{Tian:2017wrba} for its proof):
\begin{lemma}
Given an equivalence relation $R$ defined on a type, and two sets $A, B$
of elements in this type, 
if $A$ is finite, $B$ is infinite, and all elements
in $B$ belong to distinct equivalence classes, then there exists an element $k$ in $B$
which is not equivalent to any element in $A$:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}. \HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}. \HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}\hfill[INFINITE_EXISTS_LEMMA]
\end{alltt}
\end{lemma}
% \begin{proof}
%   We built an explicit mapping $f$ from $A$ to $B$\footnote{There're
%     multiple ways to prove this lemma, a simpler proof is to make a
%     reverse mapping from $B$ to the power set of $A$ (or further use
%     the Axiom of Choice (AC) to make a mapping from $B$ to $A$), then
%     the non-injectivity of this mapping will contradict the fact that
%     all elements in the infinite set are distinct. Our proof doesn't
%     need AC, and it relies on very simple truths about sets.}, for all
%   $x \in A$, $y = f(x)$ if $y \in B$ and $y$ is equivalent with
%   $x$. But it's possible that no element in $B$ is equivalent with
%   $x$, and in this case we just choose an arbitrary element as
%   $f(x)$. Such a mapping is to make sure the range of $f$ always fall
%   into $B$.

>>>>

For any \HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}, having the function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
defined on the natural numbers, we obtain a countable set of Klop processes built from the same label.
As the number of all Klop processes in this set is (countably) infinite, and
as they are all pairwise non-bisimiar,
we can always choose a number, corresponding to a Klop process,
that is non-bisimilar with any derivative of two given 
 (finite-state) processes $p$ and $q$,
even when $a$ is the only element of type $\beta$, i.e. the only label name
in $\mathscr{L}$.
This property is captured by appealing to the following set-theoreric
lamma (see~\cite{Tian:2017wrba} for its proof):
\begin{lemma}
Given an equivalence relation $R$ defined on a type, and two sets $A, B$
of elements in this type, 
if $A$ is finite, $B$ is infinite, and all elements
in $B$ belong to distinct equivalence classes, then there exists an element $k$ in $B$
which is not equivalent to any element in $A$:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}. \HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}. \HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}\hfill[INFINITE_EXISTS_LEMMA]
\end{alltt}
\end{lemma}
% \begin{proof}
%   We built an explicit mapping $f$ from $A$ to $B$\footnote{There're
%     multiple ways to prove this lemma, a simpler proof is to make a
%     reverse mapping from $B$ to the power set of $A$ (or further use
%     the Axiom of Choice (AC) to make a mapping from $B$ to $A$), then
%     the non-injectivity of this mapping will contradict the fact that
%     all elements in the infinite set are distinct. Our proof doesn't
%     need AC, and it relies on very simple truths about sets.}, for all
%   $x \in A$, $y = f(x)$ if $y \in B$ and $y$ is equivalent with
%   $x$. But it's possible that no element in $B$ is equivalent with
%   $x$, and in this case we just choose an arbitrary element as
%   $f(x)$. Such a mapping is to make sure the range of $f$ always fall
%   into $B$.
